formula1: the points system

### 2025-03-04 inst/formula1_points.Rmd
code does not work with new-style ranktables

```{r howclosetoreality,cache=TRUE}
maxp(rank_likelihood(random_table)) # should be close to mL2017
```

```{r checkagain}
a <- random_table
class(a) <- "matrix"
a[] <- points[a]
a
p <- colSums(a)
p
rando <- order(p,decreasing=TRUE)
rando
```

@@

```{r thuswesee}
jj <- sort(p,decreasing=TRUE)
jj
names(jj)
```

```{r,dothework,cache=TRUE}
n <- 200
goodness <- rep(-Inf,n)
synthetic_winner_points     <- rep("",n)
synthetic_winner_likelihood <- rep("",n)
f <- function(x,y){sum(cumprod(x==y))}
for(i in seq_len(n)){
	a <- rrank(n=ncol(f2017), p=mL2017)
	jj <- a
	class(jj) <- "matrix"
	jj[] <- points[jj]
	p <- colSums(jj)  # synthetic points
	names(p) <- names(mL2017)
	synthetic_rank_points <- names(sort(p,decreasing=TRUE))
	synthetic_winner_points[i] <- synthetic_rank_points[1]

>>>>

```{r howclosetoreality,cache=TRUE}
maxp(suppfun(random_table)) # should be close to mL2017
```

```
a <- random_table
class(a) <- "matrix"
a[] <- points[a]
a
p <- colSums(a)
p
rando <- order(p,decreasing=TRUE)
rando
```

@@

```
jj <- sort(p,decreasing=TRUE)
jj
names(jj)
```

```
n <- 200
goodness <- rep(-Inf,n)
synthetic_winner_points     <- rep("",n)
synthetic_winner_likelihood <- rep("",n)
f <- function(x,y){sum(cumprod(x==y))}
for(i in seq_len(n)){
	a <- rrank(n=ncol(f2017), p=mL2017)
	jj <- a
	class(jj) <- "matrix"
	jj[] <- points[jj]
	p <- colSums(jj)  # synthetic points
	names(p) <- names(mL2017)
	synthetic_rank_points <- names(sort(p,decreasing=TRUE))
	synthetic_winner_points[i] <- synthetic_rank_points[1]
